In this chapter, we provide a detailed walkthrough of encoding the itemset mining problem into a SAT problem.
We begin by establishing variable conventions and introducing constraints, gradually transitioning to converting these constraints into Conjunctive Normal Form (CNF) using the standard method.
Along the way, we discuss the limitations of the standard method, particularly in handling large datasets or high support thresholds.
Our goal is to equip readers with a clear understanding of the SAT encoding process for itemset mining and the challenges it entails.

\section{Technical background}
\subsection{Propositional Expression}
Propositional logic formulas or propositional expressions are constructed from variables
and logical operators AND (conjunction), OR (disjunction), NOT (negation), and
parentheses.

\textbf{Proposition}: Each statement that can be either true or false is called a proposition,
denoted by letters such as P, Q, R, ...

\textbf{Negation}

The negation (NOT) of a proposition P is denoted by $\lnot$ P. The negation
is true when P is false.

Truth table:
\begin{table}[H]
    \centering
    \caption{Truth table of negation (NOT)}
    \label{tab:truth_table_negation}
    \begin{tabular}{|c|c|}
        \hline
        P & $\lnot$ P \\
        \hline
        T & F         \\
        F & T         \\
        \hline
    \end{tabular}
\end{table}

\textbf{Conjunction}

The conjunction (AND) of two propositions P and Q is denoted by P
$\land$ Q. The conjunction is true only when both P and Q are true.

Truth table:
\begin{table}[H]
    \centering
    \caption{Truth table of conjunction (AND)}
    \label{tab:truth_table_conjunction}
    \begin{tabular}{|c|c|c|}
        \hline
        P & Q & P $\land$ Q \\
        \hline
        T & T & T           \\
        T & F & F           \\
        F & T & F           \\
        F & F & F           \\
        \hline
    \end{tabular}
\end{table}

\textbf{Disjunction}

The disjunction (OR) of two propositions P and Q is denoted by P $\lor$ Q.
The disjunction is true when at least one of P and Q is true.

Truth table:
\begin{table}[H]
    \centering
    \caption{Truth table of disjunction (OR)}
    \label{tab:truth_table_disjunction}
    \begin{tabular}{|c|c|c|}
        \hline
        P & Q & P $\lor$ Q \\
        \hline
        T & T & T          \\
        T & F & T          \\
        F & T & T          \\
        F & F & F          \\
        \hline
    \end{tabular}
\end{table}

\textbf{Implication}

The implication of two propositions P and Q is denoted by P $\rightarrow$ Q.
The implication is false only when P is true and Q is false.

Truth table:
\begin{table}[H]
    \centering
    \caption{Truth table of implication}
    \label{tab:truth_table_implication}
    \begin{tabular}{|c|c|c|}
        \hline
        P & Q & P $\rightarrow$ Q \\
        \hline
        T & T & T                 \\
        T & F & F                 \\
        F & T & T                 \\
        F & F & T                 \\
        \hline
    \end{tabular}
\end{table}

\textbf{Biconditional}

The biconditional of two propositions P and Q is denoted by P $\leftrightarrow$ Q.
The biconditional is true when both P and Q have the same truth value.

Truth table:
\begin{table}[H]
    \centering
    \caption{Truth table of biconditional}
    \label{tab:truth_table_biconditional}
    \begin{tabular}{|c|c|c|}
        \hline
        P & Q & P $\leftrightarrow$ Q \\
        \hline
        T & T & T                     \\
        T & F & F                     \\
        F & T & F                     \\
        F & F & T                     \\
        \hline
    \end{tabular}
\end{table}

\subsection{Conjunction Normal Form (CNF)}

A propositional formula is in conjunctive normal form (CNF) if it is a conjunction of clauses, where each clause is a disjunction of literals. A literal is a propositional variable or its negation.
The standard form of CNF is
\begin{equation*}
    (P_1 \lor P_2 \lor ... \lor P_n)_1 \land ... \land (Q_1 \lor Q_2 \lor ... \lor Q_m)_p \quad n,m,p \geq 1
\end{equation*}

Sample truth table (only for P and Q and R):
\begin{table}[H]
    \centering
    \caption{Truth table of CNF}
    \label{tab:truth_table_cnf}
    \begin{tabular}{|c|c|c|c|}
        \hline
        P & Q & R & (P $\land$ Q) $\land$ R \\
        \hline
        T & T & T & T                       \\
        T & T & F & F                       \\
        T & F & T & F                       \\
        T & F & F & F                       \\
        F & T & T & F                       \\
        F & T & F & F                       \\
        F & F & T & F                       \\
        F & F & F & F                       \\
        \hline
    \end{tabular}
\end{table}

\subsection{Technical background of Itemset Mining}
Firstly, we establish several symbols to represent the itemset mining problem.
These symbols aid in formalizing the problem and defining key concepts.
For instance, we denote:
\begin{itemize}
    \item \textbf{$\Omega$}: a set of all items
    \item \textbf{$I$}: an itemset in $\Omega$, where $I \subseteq \Omega$
    \item \textbf{$T_i$}: a transaction identifier. For $T_i$ = $(i,I)$
    \item \textbf{$D$}: a transaction database, where $D$ contains a set of transactions, $D = \{T_1, T_2, ..., T_n\}$
    \item \textbf{$Supp(I, D)$}: the support of itemset $I$ in database $D$, where $Supp(I, D)$ is the number of transactions in $D$ that contain $I$
\end{itemize}
For example, in table \ref{tab:example_dataset_in_real},
we can present the dataset as a transaction database $D$.

Let $a = apple, b = banana, c = cherry, d = mango$.
Then we have database transactions in binary format as shown in table \ref{tab:example_dataset_convert_to_binary}.

\begin{table}[H]
    \centering
    \caption{Sample dataset of transactions in binary format}
    \label{tab:example_dataset_convert_to_binary}
    \begin{tabular}{|c| c c c c |}
        \hline
        \textbf{Tid} & \textbf{a} & \textbf{b} & \textbf{c} & \textbf{d} \\
        \hline
        1            & 1          & 1          & 1          & 0          \\
        2            & 1          & 0          & 0          & 1          \\
        3            & 1          & 0          & 1          & 0          \\
        4            & 0          & 0          & 1          & 1          \\
        5            & 1          & 0          & 1          & 1          \\
        \hline
    \end{tabular}
\end{table}

\begin{itemize}
    \item $\Omega$ is \{apple, banana, cherry, mango\}
    \item $I$ can be \{apple\}, \{apple, mango\}, \{apple, mango, cherry\}, ...
    \item $D$ = \{(1, \{apple, banana, cherry\}), (2, \{apple, mango\}), (3, \{apple, cherry\}), (4, \{mango, cherry\}), (5, \{apple, mango, cherry\})\}
    \item $T_1$ = (1, \{apple, banana, cherry\}), $T_2$ = (2, \{apple, mango\}), $T_3$ = (3, \{apple, cherry\}),...
    \item $Supp(\{apple, cherry\}, D)$ = 3, $Supp(\{apple\}, D)$ = 4,...
\end{itemize}
Let $\lambda$ be the minimum support threshold,
the frequent itemset mining problem is to find all itemsets $I$ such that $Supp(I, D) \geq minsup$. In general, it can present by:

\begin{center}
    $FIM(D,\lambda)$ = \{I $\subseteq \Omega$ $|$ $Supp(I, D) \geq \lambda$\}
\end{center}

One of the major challenges in itemset mining is the potential exponential growth of the output, even when using condensed representations of patterns.
